Sparse Function-space Representation \\ of Neural Networks

### 2023-05-11 paper/main.tex

\textbf{Neural network to GP} Our goal is to find a kernel from which to build a sparse Gaussian process model. If we had the following function parameterization $g(\vx) = \phi(\vx)^\top \vw$ where $\phi(\vx)$ is a feature map, we can convert from weight space prior to function space prior giving the following kernel $\kappa(\vx, \vx) = \delta^{-1} \phi(\vx) \phi(\vx)^\T$ see \citep{rasmussen2006gaussian} for details. We can approximate the feature map of the neural network  $f_\weights(\mathbf{x}_{i})$  by using the Jacobian at $\weights^*$ giving thus our GP prior becomes:
\begin{align} \label{eq-laplace-approx-function-space}
  % \transitionFn_{\weights_{i}}(\cdot) \sim \mathcal{N} \left( \mu_{\weights_{i}^{*}}(\cdot), K_{\weights_{i}^{*}}(\cdot, \cdot') \right) \qquad
  g(\vx_i) \sim \mathcal{N} \left( \mu(\vx_i), k(\vx_i, \vx_i) \right) 
  % \mu_{\weights_{i}^{*}}(\cdot)
  \mu(\cdot)
  = 0 \quad
  % = f(\cdot ;\weights^{*}) \quad
  % K_{\weights_{i}^{*}}(\cdot, \cdot')
  k(\mathbf{x}, \mathbf{x}')
  = \frac{1}{\gamma^{2}} \Jac{\weights^*}{\mathbf{x}}\Jac{\weights^*}{\mathbf{x}'}^\top,
\end{align}
where the kernel is the neural tangent kernel (NTK) ,with Jacobian given by $\Jac{\weights}{\mathbf{x}} := \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$. Alternatively we could have followed the derivation in \citet{immerImprovingPredictionsBayesian2021} where we perform a local linearization of the neural network prediction function $f^{\textrm{lin}}$

\textbf{Dual Gaussian Process} A Gaussian process (GP) is a prior over functions $f \sim \GP(\mathbf{0}, \kappa(\cdot, \cdot))$. The prior is characterized by a covariance kernel function $\kappa(\vx,\vx')$, where $\vx, \vx'$ are input vectors in $\R^{\mathrm{D}}$. Once combined with a data set ${\mathcal{D} = \{(\vx_i, y_i)\}_{i=1}^n}$ with $n$ examples, each modelled by the likelihood $p(\vy_i \mid \vf_i)$ at function $\vf_i = f(\vx_i)$\, we can form a posterior proccess using multivariate conditioning. The drawbacks of GPs reside in their lack of scaling to large datasets and non-tractability with non-Gaussian likelihoods.

>>>>

\textbf{Neural network to GP prior} Our goal is to find a kernel from which to build a sparse Gaussian process model. If we had the following function parameterization $g(\vx) = \phi(\vx)^\top \vw$ where $\phi(\vx)$ is a feature map, we can convert from weight space prior to function space prior giving the following kernel $\kappa(\vx, \vx) = \delta^{-1} \phi(\vx) \phi(\vx)^\T$ see \citep{rasmussen2006gaussian} for details. We can approximate the feature map of the neural network  $f_\weights(\mathbf{x}_{i})$  by using the Jacobian at $\weights^*$ thus our GP prior becomes:
\begin{align} \label{eq-laplace-approx-function-space}
 g(\vx_i) \sim \mathcal{N} \left( \mu(\vx_i), k(\vx_i, \vx_i) \right) 
  \mu(\cdot)
  = 0 \quad
  k(\mathbf{x}, \mathbf{x}')
  = \frac{1}{\delta} \Jac{\weights^*}{\mathbf{x}}\Jac{\weights^*}{\mathbf{x}'}^\top,
\end{align}
where the kernel is the neural tangent kernel (NTK) ,with Jacobian given by $\Jac{\weights}{\mathbf{x}} := \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$. Alternatively we could have followed the derivation in \citet{immerImprovingPredictionsBayesian2021} where we perform a local linearization of the neural network prediction function $f^{\textrm{lin}}_{\vw^*}(\vx) = f_{\vw^*}(\vx) + \Jac{\weights^*}{\mathbf{x}} (\vw - \vw^*)$. The difference with our GP prior in \cref{eq-laplace-approx-function-space} would be a slightly different linear

\textbf{Dual Gaussian Process} A Gaussian process characterizes a distribution over functions in terms of the first two moment. Seminal work by \citet{}

A Gaussian process (GP) is a prior over functions $f \sim \GP(\mathbf{0}, \kappa(\cdot, \cdot))$. The prior is characterized by a covariance kernel function $\kappa(\vx,\vx')$, where $\vx, \vx'$ are input vectors in $\R^{\mathrm{D}}$. Once combined with a data set ${\mathcal{D} = \{(\vx_i, y_i)\}_{i=1}^n}$ with $n$ examples, each modelled by the likelihood $p(\vy_i \mid \vf_i)$ at function $\vf_i = f(\vx_i)$\, we can form a posterior proccess using multivariate conditioning. The drawbacks of GPs reside in their lack of scaling to large datasets and non-tractability with non-Gaussian likelihoods.
